### 2020-03-26 CalNotes.tex
Theorem 3.15 proof rewritten

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

 In particular, in light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta^2 (B_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and therefore studying the right hand side of the approximate equality above is the goal of the upcoming discussion. The following result, whose proof is in Appendix \ref{ap:ProofsDeltaZeta}, gives a first characterization.

@@

\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple} hold. Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$. If $\widetilde M$ is invertible, then
		\begin{equation}
		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in probability},
		\end{equation}
		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
\end{theorem}
\begin{proof}
	Let us introduce the notation
	\begin{equation}
	\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
	\end{equation}
	where
	\begin{equation}
	\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
	\end{equation}
	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
	\begin{equation}
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
	\end{equation}
	Using Lemma \ref{prop:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
	\begin{equation}
	\begin{aligned}
	\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
	&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta B_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
	&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
	\end{aligned}
	\end{equation}
	where and $\E$ denotes the expectation with respect to the Wiener measure and
	\begin{equation}
	\begin{aligned}
	J_1^\epl(t) &= \delta \E \left[ (B_t^\epl)^2 V''(Z_t^\epl) \right], \\
	J_2^\epl(t) &= 2 \E \left[ B_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
	J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
	\end{aligned}
	\end{equation}
	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple}, we get
	\begin{equation}
	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
	\end{equation}
	and, by Lemma \ref{lem:quadruple_convergence} and due to \eqref{eq:quadruple_remainder}, we obtain
	\begin{equation}
	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
	\end{equation}
	Moreover, due to \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
	\begin{equation}
	\begin{aligned}
	\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
	\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
	\end{aligned}
	\end{equation}
	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
	\begin{equation}
	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] = \mathcal M_0.
	\end{equation}
	Therefore
	\begin{equation}
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\rho^0} [V''(X)],
	\end{equation}
	and, finally, an integration by parts yields
	\begin{equation}
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \frac1\Sigma \mathcal M_0 A = A,
	\end{equation}
	which implies the desired result.
\end{proof}

>>>>

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}\label{eq:DefMTilde}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

In light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta^2 (B_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and therefore studying the right hand side of the approximate equality above is the goal of the upcoming discussion. The following result, whose proof is in Appendix \ref{ap:ProofsDeltaZeta}, gives a first characterization.

@@

\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple} hold. Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$. If $\widetilde M$ is invertible, then
		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in probability},
		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
\begin{proof}
	Let us introduce the notation
	\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
	Using Lemma \ref{prop:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
	\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
	&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta B_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
	&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
	where $R(\epl, \delta)$ is given in Proposition \ref{prop:zeta}, $\E$ denotes the expectation with respect to the Wiener measure and
	J_1^\epl(t) &= \delta \E \left[ (B_t^\epl)^2 V''(Z_t^\epl) \right], \\
	J_2^\epl(t) &= 2 \E \left[ B_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
	J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple} and Lemma \ref{lem:quadruple_convergence} we get
	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) &= \lim_{\epl \to 0}\delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl) \right] \\
	&= \lim_{\epl \to 0} \left(\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta)\right)\\
	&= \Sigma \E^{\rho^0} [V''(X)].
	Let us now consider $J_2^\epl(t)$. Considering Hölder conjugates $p,q,r$ the Hölder inequality yields
		\abs{J_2^\epl(t)} \leq \E[(B_t^\epl)^p]^{1/p}\E[R(\epl,\delta)^q]^{1/q}\E[V''(Z^\epl)^r]^{1/r}.
	Now, we can bound the first two terms with \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, respectively. The third term is bounded due to Assumption \ref{as:regularityZeta} and Lemma \ref{lem:bounded_momentZ}. Hence, we have
		\abs{J_2^\epl(t)} \le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right).
	We consider now $J_3^\epl(t)$. The Hölder inequality yields for conjugates $p$ and $q$
		\abs{J_3^\epl(t)} \le \E[R(\epl, \delta)^{2p}]^{1/p} \E[V''(Z_t^\epl)^q]^{1/q},
	which, reasoning as above, yields
		\abs{J_3^\epl(t)} \le C \left( \delta + \epl^2 \delta^{-1} \right).
	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, and due to geometric ergodicity the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$. Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
	Therefore
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\rho^0} [V''(X)],
	and, finally, an integration by parts yields
	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \frac1\Sigma \mathcal M_0 A = A,
	which implies the desired result.
